\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath,xspace}
\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%
\newcommand{\nome}[1]{#1}
\newcommand{\cognome}[1]{#1}
\newcommand{\person}[2]{\nome{#1}\ \cognome{#2}\xspace}
\newcommand{\CDG}{\person{Cinzia}{Di Giusto}}
\newcommand{\EF}{\person{Enrico}{Formenti}}
\newcommand{\JMF}{\person{Jean-Marc}{Fédou}}
\newcommand{\AMU}{\person{Alexandre}{Muzy}}
\newcommand{\AM}{\person{Arnaud}{Malapert}}
\newcommand{\JCR}{\person{Jean-Charles}{Régin}}
%

\title{Activity Report - 2018}
\author{MDSC}

\begin{document}
\maketitle

\section{Prizes, Awards, and Other Distinctions}
\begin{itemize}
 \item 
\end{itemize}

\section{Conference, workshop and schools organization}
\begin{itemize}
 \item Bruno Martin:
 \begin{itemize}
     \item Organizer of the first \href{http://univ-cotedazur.fr/events/ecole-de-cybersecurite}{\'Ecole de cybersécurité à Sophia}
 \end{itemize}
\end{itemize}

\section{Industrial transfer}
\begin{itemize}
 \item
\end{itemize}


\section{Invited researchers}

\begin{itemize}
 
 \item Mauricio Cano, University of Groningen  (19 February-20 April 2018) 
 
 
\end{itemize}

\section{Invited Team members}

\begin{itemize}

 \item Cinzia Di Giusto:
 \begin{itemize}
  \item University of Groeningen, The Netherlands, 1 week July 2018
\end{itemize}
\end{itemize}

\section{Invited Talks}

\begin{itemize}
 \item Bruno Martin:
 \begin{itemize}
     \item Invited talk at \href{https://is-candar.org/afca18}{AFCA-CANDAR} \emph{Pseudo-random sequence generation with cellular automata}.
 \end{itemize}
\end{itemize}

\section{Project Reviewing and Evaluation Committees}

\begin{itemize}
\item
 \end{itemize}
 


\section{Program Committees}

\begin{itemize}


\item Enrico Formenti, 
\begin{itemize}
\item AUTOMATA 2018 (PC Member), Gents, Belgique.
\end{itemize}
\item Cinzia Di Giusto, EXPRESS 2018 (PC member) Beijing, China.
 \item Bruno Martin:
 \begin{itemize}
     \item 
 \end{itemize}
\end{itemize}

\section{Editorial Boards}
\begin{itemize}

 \item Enrico Formenti, associated editor of:
 \begin{itemize}
 \item \href{http://www.oldcitypublishing.com/journals/jca-home/}{Journal of Cellular Automata} (Old City Publishing), since 200X.
 \item \href{http://www.springer.com/computer/theoretical+computer+science/journal/11047}{Natural Computing} (Natural Computing), since 20XX.
 \item \href{http://www.jalc.de}{Journal of Languages, Automata and Combinatorics}, since 2016.
 \end{itemize}
 \item \JCR, Associated editor \href{https://link.springer.com/journal/10601}{Constraints} journal (Springer) since 2015
\end{itemize}

\section{Scientific Culture Divulgation}
\begin{itemize}
\item 
\end{itemize}

\section{Patents}
\begin{itemize}
 \item
\end{itemize}

\section{HDR}
\begin{itemize}
 \item
\end{itemize}

\section{Thèses soutenues dans l'équipe}
\begin{itemize}
 \item Luca Mariot, Cellular Automata, Boolean Functions and Combinatorial Designs, March 9th, 2018.
\end{itemize}

\section{Participation in External PhD and HDR Juries}
\begin{itemize}

\item Enrico Formenti:
\begin{itemize}
\item jury member of the evaluation committee (4 PhD), Università degli Studi di Milano-Bicocca, Milan (Italie), March 8th 2018.
    \item "examinateur" of the PhD thesis  of Mohammed Bakiri, Université de Franche-Comté, Belfort, January 8th 2018.
    \end{itemize}

\end{itemize}

\section{Involvement in Master Programs}
\begin{itemize}
 
 \item Master 2 RIF, person in charge:, Enrico Formenti.
 \item Master IDEX Program MoDSU, Bruno Martin, membre du comité de pilotage.
 
 \item Masters Informatiques, person in charge: \JCR
 \item Master 1 Informatique, IFI, MBDS, RIF, person in charge: \JCR
\end{itemize}


\end{document}